Comparison of clusters to cell types for `r params$library_id`

### 2024-12-05 analyses/cell-type-ewings/template_notebooks/clustering-workflow/02-clustering-celltypes.Rmd
Apply suggestions from code review
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

- Algorithm: `r params$algorithm` 
- Objective function: `r params$objective_function`
- Resolution: `r params$resolution`

@@

# read in clustering results 
clusters_df <- readr::read_tsv(params$cluster_results_file) |> 
  # filter to specified parameters 
  dplyr::filter(algorithm == params$algorithm,
                objective_function == params$objective_function,
                resolution == params$resolution) |> 
  # modify the nn column to be a character for easy plot labels
  dplyr::mutate(cluster = as.factor(cluster),
                nn_char = glue::glue("nn-{nn}") |> 
                  # make sure 5 comes first 
                  forcats::fct_relevel("nn-5", after = 0)) |> 
  # rename barcode column for joining
  dplyr::rename(barcodes = "cell_id")
```

>>>>

- Algorithm: `r params$algorithm` 
- Objective function (if Leiden): `r params$objective_function`
- Resolution: `r params$resolution`

@@

# read in clustering results 
clusters_df <- readr::read_tsv(params$cluster_results_file) |> 
  # filter to specified parameters 
  dplyr::filter(algorithm == params$algorithm,
                objective_function == params$objective_function,
                resolution == params$resolution) |> 
  # modify the nn column to be a character for easy plot labels
  dplyr::mutate(cluster = as.factor(cluster),
                # make sure 5 comes first 
                nn_char = forcats::fct_relevel(glue::glue("nn-{nn}"), "nn-5", after = 0)
         ) |>
  # rename barcode column for joining
  dplyr::rename(barcodes = "cell_id")
```
